### 2019-01-05 Sections/essay_the_era_of_quantum_supremacy.tex
Adding image cropping
Resized figs for 1 column
Random number fig
Added quotes

\section{The era of quantum supremacy} \label{sec:era_quant} \index{Quantum supremacy}

@@

\begin{figure}[!htbp]
\includegraphics[width=0.475\textwidth]{moores_law}
\captionspacefig \caption{Historical trends in classical computing power for both PCs and top-end supercomputers, with an extrapolation 5 years into the future. The close fit to consistent exponential growth in performance over time is apparent from the logarithmic scale.} \label{fig:moores_law}
\end{figure}

@@

%As a comparison we compare this to the \textsc{BosonSampling} \comment{NO BOSON-SAMPLING. MAKE SUPERIMPOSED PLOT COMPRISING ALL ARCHITECTURES AND DEVELOPMENTS. TRY TO EXTRAPOLATE} (Sec.~\ref{sec:BS})\index{Boson-sampling} model for restricted quantum computation, as it is perhaps the most plausible candidate for the first demonstration of quantum computational supremacy. The relationship between \textsc{BosonSampling} photon-number and classical equivalent processing power is shown in Fig.~\ref{fig:moores_super}.

%\begin{figure}[!htbp]
%\includegraphics[width=0.475\textwidth]{moores_super}
%\captionspacefig \caption{Relationship between photon-number and classical equivalent FLOPS for `scattershot' \textsc{BosonSampling}. The annotated red data-points show several points of interest, taking a Moore's Law extrapolation of classical computing power 5 years into the future for desktop PCs and top-end high-performance computers, as well as an order of magnitude greater performance respectively. We use these as indicators of the post-classical era.} \label{fig:moores_super}
%\end{figure}

%\comment{Based on these extrapolations}, \cite{CYLu} \comment{(Need to revise the numbers, cite Montanaro et al. on classical simulation of boson-sampling)} \comment{made the prediction that a \textsc{BosonSampling} computer could outperform top-end supercomputers of 5 years into the future by an order of magnitude (a fairly reasonable benchmark for usage of the term `post-classical') using just \mbox{$\sim 24$} photons. Given that present-day experimental efforts have recently reached 10 photons \cite{bib:tenPhotEnt}, with great ambitions to scale up further, it is to be expected that the post-classical era is imminent. Whilst it is difficult to predict exactly when technology will allow a bank of 24 high-fidelity, highly-indistinguishable, push-button (or heralded) single-photon sources operating in parallel, it seems fair to predict that the timescale will be on the order of years rather than decades.}

%\comment{However, be weary that we are being a little optimistic with this statement, since \textsc{BosonSampling} is not universal for quantum computation, and doesn't even have any known practical uses, i.e it's post-classical and that's about it! It would be more helpful to consider prospects for \textit{universal} quantum computation.}

>>>>

\section{The era of quantum supremacy} \label{sec:era_quant} \index{Quantum supremacy}\index{SJW}

\famousquote{No matter how tiny you look, you can lead huge men if you have what the huge men don't have.}{Michael Bassey Johnson}
\newline

@@

\begin{figure}[!htbp]
\if 3\pubmode
\includegraphics[clip=true, width=0.7\textwidth]{moores_law}
\else
\includegraphics[clip=true, width=0.475\textwidth]{moores_law}
\fi
\captionspacefig \caption{Historical trends in classical computing power for both PCs and top-end supercomputers, with an extrapolation 5 years into the future. The close fit to consistent exponential growth in performance over time is apparent from the logarithmic scale.} \label{fig:moores_law}
\end{figure}

@@

### 2019-01-05 Sections/optimising_the_world.tex
Added quotes

In this incarnation of the map colouring problem, a valid colouring specifies a set of transmission frequencies that avoid interregional signal interference, and the chromatic number specifies the smallest possible radio spectrum\index{Radio spectrum} that must be allocated\footnote{Spectrum is worth a lot of money!}.

@@

\subsection{Approximate optimisation}\index{Approximate optimisation}

>>>>

In this incarnation of the map colouring problem, a valid colouring specifies a set of transmission frequencies that avoid interregional signal interference, and the chromatic number specifies the smallest possible radio spectrum\index{Radio spectrum} that must be allocated\footnote{Spectrum is a scarce resource\index{Scarcity}, in high demand, and worth a lot of money!}.

@@

\subsection{An example of a poorly constructed joke}\index{Jokes}

\famousquote{How many apples grow on a tree? All of them.}{Dad}
\newline

A number of years ago there was a popular quantum computing joke circulating the internet. It went along the lines of:
\\
\\
\textit{Q:\,\,What happens when two quantum computers play chess?}\\
\textit{A:\,\,White e3, black resigns.}
\\

This joke is of course based on the assumption that quantum computers can efficiently and optimally solve the chess problem, foreseeing the entire future of a game, and determining the perfect optimal next move. Thus, after making the optimal first move `e3', black concedes that he cannot win.

However this is a poorly-designed joke, since it has been proven that chess is an \textbf{EXP}-complete problem\footnote{The complexity of chess is defined in the context where the game is generalised appropriately to an \mbox{$n\times n$} board, since complexity classes are all about computational scaling against problem size, and obviously any \textit{fixed} size instance of a game can be solved in $O(1)$ time (albeit with perhaps a very large constant!).}, believed to lie well outside of \textbf{BQP}, that which is efficiently solvable on quantum computers. Therefore this is a bad joke and it isn't funny.

However, although quantum computers are unlikely to be able to efficiently play chess \textit{optimally}, there may still be some room for improvement in \textit{approximating} optimal moves, to be discussed next in Sec.~\ref{sec:approx_optim}.

\subsection{Approximate optimisation}\label{sec:approx_optim}\index{Approximate optimisation}
